---
title: "Introduction to StatComp22091"
author: "22091"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp22091}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp22091__ is a simple R package and final project of 22091 for the 'Statistical Computing' course. Two functions are included, namely, _delta_i_ and _gibbs_cpp_.  



## _delta_i_

The source R code for _delta_i_ is as follows:
```{r,eval=FALSE}
delta_i = function(data_i, big_delta_symbolic, params_first,  params_second, param_vals 
){
  
  # Iterate through the symbolic expression for Delta and 
  # evaluate each element numerically.
  big_delta = matrix(NA, nrow = length(params_second), ncol = length(params_first))
  env = as.list(c(data_i, param_vals))
  for (r in 1:nrow(big_delta)) {
    for (c in 1:ncol(big_delta)) {
      big_delta[r,c] = eval(
        big_delta_symbolic[r,c][[1]],
        env = env)
    }
  }
  
  return(big_delta)
}
```

We observe two types of responses (Wi, Yi) that are independent and identically distributed and two types of covariates, (Xi,Zi). There are two parameters, θ and β.relationship between W and (X,Z, θ) is described by a model which has an estimating function Ψ(W, X,Z, θ). The relationship between Y and (X,Z, β, θ) is described by a model
that has an estimating function K(Y, X,Z, β, θ). We define θ and β as the solutions to E{Ψ(W, X,Z, θ)} = 0 and E{K(Y, X,Z, β, θ)} = 0 respectively.

And this function is one of the functions used to estimate the model:to calculate the delta.


The source Rcpp code for _gibbs_cpp_ is as follows:
```{r eval=FALSE}
NumericMatrix gibbs_cpp(int N,double mu1,double mu2,double sigma1,double sigma2,double rho){
  NumericMatrix X(N,2);
  double s1,s2;
  s1=sqrt(1-pow(rho,2))*sigma1;
  s2=sqrt(1-pow(rho,2))*sigma2;
  X(0,0)=mu1;
  X(0,1)=mu2;
  double x1,x2,m1,m2;
  for(int i=1;i<N;i++){
    x2=X(i-1,1);
    m1=mu1+rho*(x2-mu2)*sigma1/sigma2;
    X(i,0)=rnorm(1,m1,s1)[0];
    x1=X(i,0);
    m2=mu2+rho*(x1-mu1)*sigma2/sigma1;
    X(i,1)=rnorm(1,m2,s2)[0];
  }
  return(X);
}
```

compared with gibbs using R, gibbs_cpp is faster.
